The fraction of polar aligned circumbinary disks

### 2025-04-14 src/tex/response.tex

    \begin{response}
        {L473: Syntax/repetition issue. Please rephrase.}
        We have fixed the issue by clarifying that we are translating the precession timescale from code units to physical units.
    \end{response}

    \begin{response}
        {Fig. 8: The bottom part of this figure could be further commented in Sect. 6.1.}
        We have added text in Section 6.1 discussing this panel.
    \end{response}

    \begin{response}{
        L532: Bohn+2022 could be a relevant reference to add here.
    }
     Thank you for the great suggestion. We have added the reference.   
    \end{response}

    \begin{response}
        {L580: I would conclude the discussion (or add to the conclusion) that, besides imposing constraints on the disc radial extend and j, the two studied mechanisms (disc breaking and self-gravity) are expected to lower the fraction of polar CBDs. If I understood correctly, large values of j and radially extended discs are unlikely to become polar (as a whole at least). Therefore, the statistical relevance/weight of this subgroup of discs should be less important at the overall polar CBD population level. This could be briefly commented at the end.}

        This is a great suggestion, however the overall effect is more complicated. For disks that break, $f_\text{polar}$ being ``the fraction of disks that evolve to a polar configuration'' may be less relevant than ``the fraction of systems that host a polar disk''. The main effect of disk breaking is that the alignment of the inner disk happens more quickly, reducing the fraction of systems which have neither a polar nor coplanar disk. The main effect of gravitational instability is that massive disks must be more radially extended, which could possibly lead to warps and breaks. The total effect likely would be that a single extended disk evolves into multiple disks with various degrees of alignment, whether that be polar or coplanar. We have added text at the end of the discussion to highlight these effects.
    \end{response}

### 2025-04-14 src/tex/ms.tex
Change discussion of combined breaking and grav effects

\RR{
    Together, the processes of disk breaking and gravitational instability lead to disks that are less massive and less radially extended. These processes should lower the statistical weight of massive, extended disks and make $f_\text{polar}$ more heavily dependent on narrower disks with small masses (low $j$). The dynamical states of these disks are more strongly dependent on $e_\text{b}$ and evolve to a stable configuration on shorter timescales. Without an underlying binary eccentricity distribution it is difficult to say if $f_\text{polar}$ increases or decreases when these effects are considered. However, the fraction of disks whose lifetimes are shorter than their alignment timescales would be reduced, and we would expect to see fewer disks outside of polar or coplanar configurations. 
}

@@

We also discuss the limitations of our methods. First, we look at the effect of finite disk lifetime on the ability for a disk to complete its evolution to a stationary state. Disks with long evolutionary timescales remain with orbital parameters near their initial conditions for their entire lifetimes. We also look at limitations imposed by the fact that real disks are not geometrically narrow rings, but have some radial extent. Real disks are likely to break if their radial extent is too large, and will become gravitationally unstable if all of their mass in concentrated in too narrow of a ring. These two effects impose constraints on the relationship between $r_\text{in}$, $r_\text{out}$, and $j$.
\RR{
These results for $f_\text{polar}$ can be tested through population-level observations of circumbinary disk systems. In practice, however, the mutual inclination between the disk and its binary host can be difficult to constrain, and therefore polar disks can be difficult to distinguish from coplanar. Known misaligned disks rely on fortunate geometry to constrain the mutual inclination, such as an eclipse of a nearby binary in the case of V773 Tau B \citep{kenworthy2022}. However, $f_\text{polar}$ could be statistically constrained by looking for polar disks around young eclipsing binaries because the binary-observer inclination is known. Imaging of a face-on disk in such systems would confirm a polar configuration. However, for an edge-on disk it would be difficult to differentiate between a coplanar and polar due to a degeneracy in viewing angle. A carefully done survey of a large population of eclipsing binaries \citep[e.g., those found by the Kepler Mission][]{kirk2016} would likely constrain the fraction of polar circumbinary disks.

A similar method has been proposed by \citet{zhang2019} to distinguish polar from coplanar planets in eclipsing binary systems via eclipse timing variations. I contrast to the imaging method suggested previously, such a method would be less expensive, have fewer degeneracies, and have many more potential targets as it would not be restricted to young systems. Additionally, it would be most sensitive to planets with small separations from their host binaries, meaning the alignment timescale for the progenitor disk would be much shorter than for those that could be resolved via imaging. Together, these two methods could provide robust constraints of $f_\text{polar}$ across many regimes of host parameters and disk separation.
}

>>>>

\RR{
    When disk breaking and gravitational instability are considered jointly it may be that $f_\text{polar}$, as calculated in this study, is not as relevant as ``the fraction of binary systems which host a polar circumbinary disk.'' Gravitational instability (if not suppressed by heating as mentioned previously) requires that massive high-$j$ disks be more radially extended, making them more susceptible to differential precession and breaking. The result is that a circumbinary system initially hosting a single, extended, misaligned disk may evolve to host a series narrower rings, with the innermost most likely to have completed its evolution to a coplanar or polar alignment.
}

@@

We also discuss the limitations of our methods. First, we look at the effect of finite disk lifetime on the ability for a disk to complete its evolution to a stationary state. Disks with long evolutionary timescales remain with orbital parameters near their initial conditions for their entire lifetimes. We also look at limitations imposed by the fact that real disks are not geometrically narrow rings, but have some radial extent. Real disks are likely to break if their radial extent is too large, and will become gravitationally unstable if all of their mass in concentrated in too narrow of a ring. These two effects impose constraints on the relationship between $r_\text{in}$, $r_\text{out}$, and $j$.

\RR{
These results for $f_\text{polar}$ can be tested through population-level observations of circumbinary disk systems. In practice, however, the mutual inclination between the disk and its binary host can be difficult to constrain, and therefore polar disks can be difficult to distinguish from coplanar. Known misaligned disks rely on fortunate geometry to constrain the mutual inclination, such as an eclipse of a nearby binary in the case of V773 Tau B \citep{kenworthy2022}. However, $f_\text{polar}$ could be statistically constrained by looking for polar disks around young eclipsing binaries because the binary-observer inclination is known. Imaging of a face-on disk in such systems would confirm a polar configuration. However, for an edge-on disk it would be difficult to differentiate between a coplanar and polar due to a degeneracy in viewing angle. A carefully done survey of a large population of eclipsing binaries \citep[e.g., those found by the Kepler Mission][]{kirk2016} would likely constrain the fraction of polar circumbinary disks.}

\RR{
A similar method has been proposed by \citet{zhang2019} to distinguish polar from coplanar planets in eclipsing binary systems via eclipse timing variations. I contrast to the imaging method suggested previously, such a method would be less expensive, have fewer degeneracies, and have many more potential targets as it would not be restricted to young systems. Additionally, it would be most sensitive to planets with small separations from their host binaries, meaning the alignment timescale for the progenitor disk would be much shorter than for those that could be resolved via imaging. Together, these two methods could provide robust constraints of $f_\text{polar}$ across many regimes of host parameters and disk separation.
}
